Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-09 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add in temporal trend plots for exposures

>>>>

Here are time trends for some different metrics:

```{r echo = FALSE}
tornado_events <- county_events(counties = my_fips, event_type = "tornado",
                                start_year = 1988, end_year = 2011) %>%
        dplyr::group_by(storm_id) %>%
        dplyr::summarize(n_counties = n()) %>%
        dplyr::mutate(year = as.numeric(gsub(".+-", "", storm_id)))

tornado_year_mean <- tornado_events %>%
        dplyr::group_by(year) %>%
        dplyr::summarize(year_mean = mean(n_counties),
                         year_tot = sum(n_counties))

a <- ggplot(tornado_events, aes(x = year, y = n_counties)) + 
        geom_point(alpha = 0.5) + 
        geom_line(data = tornado_year_mean, aes(y = year_tot), 
                   color = "blue", alpha = 0.2, size = 1) + 
        geom_point(data = tornado_year_mean, aes(y = year_tot), 
                   color = "blue", alpha = 0.2, size = 3) + 
        theme_few() + 
        xlab("Year") + ylab("Number of exposed counties")+ 
        ggtitle("Patterns in county exposure to tornado events")

flood_events <- county_events(counties = my_fips, event_type = "flood",
                                start_year = 1988, end_year = 2011) %>%
        dplyr::group_by(storm_id) %>%
        dplyr::summarize(n_counties = n()) %>%
        dplyr::mutate(year = as.numeric(gsub(".+-", "", storm_id)))

flood_year_mean <- flood_events %>%
        dplyr::group_by(year) %>%
        dplyr::summarize(year_mean = mean(n_counties),
                         year_tot = sum(n_counties))

b <- ggplot(flood_events, aes(x = year, y = n_counties)) + 
        geom_point(alpha = 0.5) + 
        geom_line(data = flood_year_mean, aes(y = year_tot), 
                  color = "blue", alpha = 0.2, size = 1) + 
        geom_point(data = flood_year_mean, aes(y = year_tot), 
                   color = "blue", alpha = 0.2, size = 3) + 
        theme_few() + 
        xlab("Year") + ylab("Number of exposed counties") + 
        ggtitle("Patterns in county exposure to flood events")

rain_events <- county_rain(counties = my_fips, rain_limit = 75, dist_limit = 500,
                              start_year = 1988, end_year = 2011) %>%
        dplyr::group_by(storm_id) %>%
        dplyr::summarize(n_counties = n()) %>%
        dplyr::mutate(year = as.numeric(gsub(".+-", "", storm_id)))

rain_year_mean <- rain_events %>%
        dplyr::group_by(year) %>%
        dplyr::summarize(year_mean = mean(n_counties),
                         year_tot = sum(n_counties))

c <- ggplot(rain_events, aes(x = year, y = n_counties)) + 
        geom_point(alpha = 0.5) + 
        geom_line(data = rain_year_mean, aes(y = year_tot), 
                  color = "blue", alpha = 0.2, size = 1) + 
        geom_point(data = rain_year_mean, aes(y = year_tot), 
                   color = "blue", alpha = 0.2, size = 3) + 
        theme_few() + 
        xlab("Year") + ylab("Number of exposed counties") + 
        ggtitle("Patterns in county exposure to rain")

wind_events <- county_wind(counties = my_fips, wind_limit = 15, 
                           start_year = 1988, end_year = 2011) %>%
        dplyr::group_by(storm_id) %>%
        dplyr::summarize(n_counties = n()) %>%
        dplyr::mutate(year = as.numeric(gsub(".+-", "", storm_id)))

wind_year_mean <- wind_events %>%
        dplyr::group_by(year) %>%
        dplyr::summarize(year_mean = mean(n_counties),
                         year_tot = sum(n_counties))

d <- ggplot(wind_events, aes(x = year, y = n_counties)) + 
        geom_point(alpha = 0.5) + 
        geom_line(data = wind_year_mean, aes(y = year_tot), 
                  color = "blue", alpha = 0.2, size = 1) + 
        geom_point(data = wind_year_mean, aes(y = year_tot), 
                   color = "blue", alpha = 0.2, size = 3) + 
        theme_few() + 
        xlab("Year") + ylab("Number of exposed counties") + 
        ggtitle("Patterns in county exposure to wind")

distance_events <- county_distance(counties = my_fips, dist_limit = 100, 
                           start_year = 1988, end_year = 2011) %>%
        dplyr::group_by(storm_id) %>%
        dplyr::summarize(n_counties = n()) %>%
        dplyr::mutate(year = as.numeric(gsub(".+-", "", storm_id)))

distance_year_mean <- distance_events %>%
        dplyr::group_by(year) %>%
        dplyr::summarize(year_mean = mean(n_counties),
                         year_tot = sum(n_counties))

e <- ggplot(distance_events, aes(x = year, y = n_counties)) + 
        geom_point(alpha = 0.5) + 
        geom_line(data = distance_year_mean, aes(y = year_tot), 
                  color = "blue", alpha = 0.2, size = 1) + 
        geom_point(data = distance_year_mean, aes(y = year_tot), 
                   color = "blue", alpha = 0.2, size = 3) + 
        theme_few() + 
        xlab("Year") + ylab("Number of exposed counties") + 
        ggtitle("Patterns in county exposure to distance")

grid.arrange(a, c, d, e, ncol = 1)
```
